---
title       : Application Son's height prediction
subtitle    : Coursera project assignment
author      : Petr Kovar
job         : Data analyst
framework   : io2012 # html5slides   # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [quiz, bootstrap]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

--- .class #id 

## Application Son's height prediction
This [application](https://pkovar-shiny.shinyapps.io/DataProduct/) provides prediction of son's height based on father's height. The prediction linear regression model was built on top of the father.son dataset provided within UsingR package.

Next slides show:

1. Summary of father.son dataset
2. Predictive lm model

       *Up to 69.5inches(177cm) model predicts higher son..*
3. Quiz. The application gives you an answer. 

---
## Dataset father.son
Data set father.son contains 1078 pairs of heights (father, son)
This is a summary.
```{r summary,echo=FALSE }
library(UsingR, verbose= FALSE, quietly=TRUE)
summary(father.son)
```

---
## Linear regression model
```{r model}
fit <- lm(sheight ~ fheight,data=father.son)
```
Intercept `r round(fit$coef[1],2)`, slope `r round(fit$coef[2],2)` 
```{r plot,echo=FALSE}
plot(father.son) 
legend("topleft",fill=c('blue','red'),legend=c('father=son','lm model'))
abline(a=0,b=1, col='blue')
abline(fit, col='red')
```

--- &radio
## Quiz

What is the predicted height (cm) of son whose father's height is 68.5 (inch)?

1. 174
2. _176_
3. 69,1
4. 67

*** .hint
Don't forget to use (cm) unit for result.

*** .explanation
The heigh is 69,1 inches which is 176 cm.







